Timeliness of security updates for Android

### 2014-02-18 securityupdates.tex
Add subsection on monetisation

>>>>

\subsection{Monetisation}
One of the key differences between smartphones and desktops is that it is easier to directly cash out on a smartphone as malware can send premium rate texts or make premium rate phone calls.
It can also steal personal data which already has semantic information associated with it, this also makes it easier to perform ransomware attacks where malware deletes this information from the device and charges a ransom for its return.
It can also do more conventional things such as use the devices for DDoS attacks and altering the ads displayed to send the fees to the malware author.
While many of these things can be done by malware which just requests the relevant permissions, root exploits make this easier, particularly for ransomware and altering the ads displayed.
